Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-03 Manuscript/manuscript.Rmd
!!!manuscript edits

4. **SMOTE** (Synthetic Minority Over-Sampling Technique) [@chawla2002smote]: This method incorporated both random under- and over-sampling. Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class. The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes. We used SMOTE to create perfectly balanced data. The `DMwR` R package v. [??? Add version number] was used to perform SMOTE.

@@

The coordinates of the corresponding 5kb resolution contact maps resulted in a total of 44948 genomic bins [??? across all chromosomes? If I do 44948*5000, I get 224740000, which is 1 billion bases less than the size of the genome. What is going on?] (Table 2). There were only 3083 (6.9%) bins that overlapped with a flanked TAD boundary [??? What is flanked TAD boundary? Why do we care?]. An increase in resolution resulted in the overall less number of genomic bins and a slighly less degree of class imbalance [??? Add exact numbers of class imbalance for each resolution] (Supplementaty Table 8). The overall average perentage of class imbalance across all data resolutions was 13.2% [??? Do not understand. I understand the ratio of #minority/#majority, but what % tells?].  After applying each resampling technique to the training sets for each data resolution, we obtained perfectly balanced classes (Figure 4). That is, the ratio of bins that overlapped with flanked TAD boundaries to bins that did not was 1:1.

@@

@@

>>>>

4. **SMOTE** (Synthetic Minority Over-Sampling Technique) [@chawla2002smote]: This method incorporated both random under- and over-sampling. Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class. The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes. We used SMOTE to create perfectly balanced data. The `DMwR` R package (version 3.4.2) [??? Add version number; !!!added version] was used to perform SMOTE.

@@

The coordinates of the corresponding 5kb resolution contact maps resulted in a total of 44948 genomic bins [??? across all chromosomes? If I do 44948*5000, I get 224740000, which is 1 billion bases less than the size of the genome. What is going on?; !!!This is only CHR1 for right now] (Table 2). There were only 3083 (6.9%) bins that overlapped with a flanked TAD boundary [??? What is flanked TAD boundary? Why do we care?]. An increase in resolution resulted in an overall decrease in the number of genomic bins, as well as a slighly less degree of class imbalance. The percentage of imbalance for each of the other resolutions were found to be  14.0%, 13.7%, and 12.2% for 25 kb, 50kb, and 100kb resolutions respectively. [??? Add exact numbers of class imbalance for each resolution; !!! added exact numbers] (Supplementaty Table 8). The overall average perentage of class imbalance across all data resolutions was 13.2% [??? Do not understand. I understand the ratio of #minority/#majority, but what % tells?].  After applying each resampling technique to the training sets for each data resolution, we obtained perfectly balanced classes (Figure 4). That is, the ratio of bins that overlapped with flanked TAD boundaries to bins that did not was 1:1.

@@

## Table 1: Class Distributions

Summary of the class distributions for the 5 kb resolution domain data, across each re-sampling technique. All re-sampling techniques yielded completely balanced classes. That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.

@@

## Table 2: Class Distributions for Other Resolutions

Summary of the class distributions for each of the other resolution domain data sets (25 kb, 50 kb, and 100 kb), across each re-sampling technique. As with the 5 kb data, all re-sampling techniques yielded completely balanced classes. That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
